MCC Predictions

### 2018-05-15 stats/ex3_comparisons.Rmd
add sketchy marg likelihood calc model

   map(function(d){ 
     // display(JSON.stringify(modelPredictions) + JSON.stringify(d.correct_inf))
      observe(modelPredictions, d.correct_inf)
    }, conditionSpecificData)

@@

>>>>

   map(function(d){ 
     // display(JSON.stringify(modelPredictions) + JSON.stringify(d.correct_inf))
      observe(modelPredictions, d.correct_inf)
      // factor(modelPredictions.score(d.correct_inf))
    }, conditionSpecificData)

@@

```{r}
bdaModel.rsa.loglikelihood <-'
var allConditions = dataFromR.allConditions
var allData = dataFromR.allData
var allPriorProbs = dataFromR.allPriorProbs

   var loglike = sum(map(function(d){ 
      return modelPredictions.score(d.correct_inf)
    }, conditionSpecificData))

  return  loglike
}, allConditions)

 return sum(loglike)
}
'
